---
title: "linear model from Web"
author: "aubrey garcia"
date: "summer 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

# methods
all varibles are numerical, so we use nummerical~numerical helper file for all three parts.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### decriptive results--scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

This plot shows that...


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The numerical results show the correlation between the two numerical variables, showing that there is a positive correlation. 

### Inferential  

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The inferential results show that the intercept p-vaule is f 0.00000000000000022 which is less that 0.05, rejecting the null hypothesis.  
sims=-4.1+0.055*arm

#### scatterplot with model fit
```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```
The p-vaules for the intercept are f 0.00000000000000022 which means that the intercept is signfigant becuase it is less than 0.05. 

The P-vaule for ARM is f 0.00000000000000022 which means that arm is signfigant. 

#### Predict at target point
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval = 'pred')
```
The sims prediction for Arm-88 is 0.71, the predicting interval is (0.7063836, )......


## Model 2 SIM~GRIP

### descriptive results--scattor plot
```{r}
plot(SIMS~GRIP,data=data)
```
The plot shows that...

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
The numerical results show there is a positive correlation between SIMS and GRIP. 

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```
  The p-vaules for the intercept are f 0.00000000000000022 which means that the intercept is signfigant becuase it is less than 0.05. 

The P-vaule for GRIP is  0.00000000000000022 which is less than 0.05, which means that Grip is signfigant.

#### predict model.2 at target point

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval = 'pred')
```
  model1.2=lm(SIMS~GRIP)
  model1.3=lm(sims~ARMS+GRIP)
  
  
#### scatterplot with model fit
```{r}
plot(SIMS~GRIP,data=data)
abline(model.2, col='blue')
```
The model fit shows that....


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

