---
title: "linear model from Web"
author: "aubrey garcia"
date: "summer 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

# methods
all varibles are numerical, so we use nummerical~numerical helper file for all three parts.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### decriptive results--scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

This plot shows that arm strength increses. 


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The numerical results show the correlation between the two numerical variables, showing that there is a positive correlation. 

### Inferential  

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The inferential results show that the intercept p-vaule is f 0.00000000000000022 which is less that 0.05, rejecting the null hypothesis.  
sims=-4.1+0.055*arm

#### scatterplot with model fit
```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```
The p-vaules for the intercept are f 0.00000000000000022 which means that the intercept is signfigant becuase it is less than 0.05. 

The P-vaule for ARM is f 0.00000000000000022 which means that arm is signfigant. 

#### Predict at target point
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval = 'pred')
```
The sims prediction for Arm=88 is -0.54, the predicting interval is (-3.12, 2.04)


## Model 2 SIM~GRIP

### descriptive results--scattor plot
```{r}
plot(SIMS~GRIP,data=data)
```
The plot shows that GRIP stength increases.

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
The numerical results show there is a positive correlation between SIMS and GRIP. 

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
  The p-vaules for the intercept are f 0.00000000000000022 which means that the intercept is signfigant becuase it is less than 0.05. 

The P-vaule for GRIP is  0.00000000000000022 which is less than 0.05, which means that Grip is signfigant.

#### predict model.2 at target point

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval = 'pred')
```
  The prediction for arm=88 is 0.53 and the interception is (-3.12, and 2.04)


## Model 3 SIM~ARM+GRIP



# Numerical(cor)

```{r}
df=data.frame(c)(SIMS=data$SIMS, GRIP=data$GRIP, ARM=data$ARM)
cor(df)
```


### Inferential  (Build 2-dimentional model.3)
`
```{r}
model1.3=lm(SIMS~ARM+GRIP, data = data)
summary(model1.3)
```
The p-vaules for the intercept are f 0.00000000000000022 which means that the intercept is signfigant becuase it is less than 0.05. 

The P-vaule for ARM+GRIP is f 0.00000000000000022 which means that arm is signfigant. 
  
  
  The p-vaule from the F fantastic is ..., this means we, the data fits the model and 

sims 5.43+0.037*ARM+0.024*GRIP

which one has a p-vaule less than 0.0


The p-vaule from the F fantastic is 0.buncha 0'

sims 5.43+0.037*ARM+0.024*GRIP

which one has a p-vaule less than 0.05


#### predict model.3 at target point
Prediction interval of sims given value of 94 for GRIP and 88 for ARM

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predSIMS=predict(model1.3, newdata, interval = 'pred')
print(predSIMS)
```
  
  The predicted SIMS score for GRIP=94, ARM=88 is  0.150 and the intersection is (-2.13, 2.43).

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
model.1 <- lm(SIMS~ARM,data=data)
#anova(model.1, model1.3)
summary.lm(model.1)
```
The anova table shows there is a difference in the models,  it shows model 2 SIMS~ARM+GRIP with RSS 188 is the better than model 1, SIM~ARM and shows the RSS is 218 . The table also shows that we reject the null hypothesis becuase the p-vaule is 0.00000004 which is less than 0.05.


The sims_arm+Grip is the best model.


### Model.2 vs Model.3

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
anova(model.2, model1.3)
```

Model SIMS~ARM+GRIP is better then model SIMS~GRIP  becuase the RSS is  188



Model 3 is best

## Informally compare Model.1 with model.2

```{r}
summary.lm(model.1)
summary
```


We conclude that model 1 is smaller than model two because it has a smaller RSS than model2.
